\plaintitle

### 2016-08-16 drafts/labor/cases.tex
notes were in the wrong file :x
various additional notes and a fix with some colors and todonotes or something
mondays

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
% \newcommand{\note}[1]{\onlyinsubfile{\ali{#1}}}

% lol oh my gosh i just discovered figlet and it's changing my life
% it's like i'm distributing warez

\section{Major Research Questions}
\ali{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

@@

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
% We will further discuss the ways that various contributions drive along these dimensions.
As we'll discuss these dimensions,
exploring the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms,
we'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\ali{At this point I'm trying to retain as much of the old content as possible,
but if the next few sections seem like I'm trying too hard to be lazy,
say so and I'll do a rewrite rather than refactoring.}

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
% lol i can't believe this worked i'm going to do this with every (sub)*section.

\subsubsection{Decomposition}\label{sec:decomposition}
Scholarship describing and exploring
the decomposition of tasks is perhaps the most established
of the previously mentioned three areas
to HCI researchers;
\citeauthor{crowdForgeKittur} specifically
drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

Much of the research in the space of designing crowd work has
sought to illustrate the potential to take highly creative or skilled work
and generate high--quality results.
Perhaps the most notable case study here can be found in
\citeauthor{foundry}'s \textit{Foundry}, which employed
``flash teams'' to achieve expert--level outcomes via thoughtful
decomposition of work as ``modular tasks''
\cite{foundry}.

Research exploring the decomposition of work more generally
--- that is, without the constraint of an employer/requester directing workers ---
has since emerged as well.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the topicality of this broader body of work will become more apparent
as we trace the parallels of crowdsourcing with piecework.

The work described thus far has illustrated myriad ways that
we can manage workers for the purpose of accomplishing complex tasks with
rapidly sourced workers from across the world.
Critically, the work's defining characteristic involves
the use of the Internet as a medium both 
to coordinate workers, as well as
to do the work itself.
But research into the ``decomposition'' of work more generally
illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger and warned of it in
\citeyear{professionalCrowdworkEthics}
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

Following this thread of work, it may be said that
much of the work in crowdsourcing has found ways of ``vertically slicing'' work
such that each person is responsible for as small a task as can be made reasonable
--- taking a minute of audio, for instance, and transcribing just that.
The aforementioned research has found many novel ways to slice work,
communicate different amounts of context of work from one worker to the next,
etc\dots
but fundamentally they follow similar patterns.
It's through this lens that we see the echoes of piecework.

@@

% Piecework's growing popularity was best documented at the turn of the \nth{20}
% by \citeauthor{riisOtherSideLives} % in his work on \citetitle{riisOtherSideLives}
% \cite{riisOtherSideLives}.

@@

%                     _            _         _                  _   _             
% __      _____  _ __| | __   __ _| |__  ___| |_ _ __ __ _  ___| |_(_) ___  _ __  
% \ \ /\ / / _ \| '__| |/ /  / _` | '_ \/ __| __| '__/ _` |/ __| __| |/ _ \| '_ \ 
%  \ V  V / (_) | |  |   <  | (_| | |_) \__ \ |_| | | (_| | (__| |_| | (_) | | | |
%   \_/\_/ \___/|_|  |_|\_\  \__,_|_.__/|___/\__|_|  \__,_|\___|\__|_|\___/|_| |_|
% lollllllllllllllll

\subsubsection{Work Abstraction}\label{sec:workAbstraction}
Decomposition allows requesters to assign tasks without concern for the broader context.
While we'll discuss this aspect of crowd work more critically later,
it's worth pointing out that discrete blocks of work containing all the relevant context for a worker
allows workers to engage with virtually any component of work without worrying that their lack of 
higher--level awareness of the goals of the requester might negatively affect their work.

\citeauthor{chilton2013cascade} perhaps best illustrated this with
\textit{Cascade} by demonstrating that it's possible to
break certain classes of tasks apart
in such a way that they yield taxonomies of various subjects,
a task previously thought to be safely within the domain of expert workers
with top--down awareness of the context of the work as a whole
\cite{chilton2013cascade}.
\citeauthor{verroios2014context} further illustrate this potential by
forming a task one might consider highly contextually dependent
--- summarizing the contents of a movie ---
in such a way that crowd workers could contribute small pieces of work without
needing to know the content of the rest of the project
\cite{verroios2014context}.

\subsubsection{Flexibility}\label{sec:flexibility}
% \msb{nothing in this subsubsection connects to the piecework literature. bring it back!}

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance.
This work both points to and embodies a broader sentiment in
both the study and practice
of crowd work that microtasks should be designed resiliently against the variability of workers,
% \msb{not sure what flexibly means here, and the rest of the sentence isn't helping me unpack it. flexibility for requester? worker? flexible algorthms?},
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance,
or a good worker's sudden departure,
would not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} identified costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together.

Given the importance of consistent work results, one might intuit that
requesters would prefer high--quality workers who can be relied upon to be available
(even for contextually independent tasks),
which would appear to contradict the benefits of flexibility already discussed;
requesters have thus made significant headway toward
``embracing error'' to allow requesters to maximize the benefits of a flexible,
even transient,
workforce.

\citeauthor{embracingErrorKrishna} offer orders--of--magnitude improvements
in various binary classification tasks
on the principle that diverse workers complete these tasks
in order to accurately inform the model on the variety of delays in response times.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of this phenomenon:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

Points to make:
  \begin{itemize}
    \item Blossoming of piecework
    \begin{itemize}
      \item high point: consultants?
      \item most cases: auto workers/etc\dots
      \item worst case: sweatshops (especially in developing nations)
    \end{itemize}
    \item what led to these outcomes?
    \begin{itemize}
      \item ``consultant'' work came out well because the work was complex;
      this made it difficult to turn into a mass market commodity.
      We see consultants ranging skill levels like
      oDesk (implementing modules) to
      Accenture (on--demand teams of consultants).
      \item auto workers,
      working in settings where capital couldn't be moved as easily
      found themselves in the same workspace as a direct
      --- if multi--stepped ---
      result to the benefits of putting people in the same place to consolidate resources.
      Moreover,
      workers had leverage over factory owners as a result of that consolidated capital;
      operating equipment required training.
      \item sweatshop workers fared the worst,
      for reasons that may seem obvious with hindsight.
      Source materials for textiles are easier to ship than mechanical components such as engines,
      making it easier for factories to relocate to developing nations
      (where cost--of--living, and consequently wages, would be lower).
      As wages, CoLAs, and QoL rise, workers begin asking for
      (and later demanding)
      higher wages and better conditions.
      But where the auto workers have leverage,
      textile workers find only a precarious economic balance now tipped by their collective action,
      spurring manufacturers to move to a new locale
    \end{itemize}
  \end{itemize}

@@

\onlyinsubfile{
\clearpage
% \section{Case Studies}
The existing body of research has shed light on on--demand labor from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the \textbf{processes} involved in making work into tasks, or discretization;
\item the outcomes (and indeed the \textbf{fallout}) of that discretization,
both on the work itself as well as the workers;
and finally
\item the \textbf{relationships} between workers and requesters of the work
--- both \textit{cooperative} and \textit{adversarial} cases.
\end{enumerate}

% \msb{I still dont' have a clear conceptual picture of what flexibility is, and what about it sets this section apart. Ranjay's stuff is about speed...? I'm confused.}

@@

Resistance against managers in piecework and factory labor settings are deeply well--explored,
but perhaps the most relevant case study to draw on here is to be found in
\citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
\cite{waldinger1996helots}.
The achievements of labor advocacy groups such as labor unions as resistant,
even adversarial organizations counter--balancing the management
is somewhat well--understood
\cite{russell1982collective,craig1992behavior}.
We argue that these threads of resistance against management in various forms
are in fact one.
}

\onlyinsubfile{
  \balance{}
  \printbibliography
}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

\section{Major Research Questions}
% \ali{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

@@

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
% As we'll discuss these dimensions,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
%

% stronger topic sentences
% boosterist

\subsubsection{Decomposition (how high can we stack the salami?)}\label{sec:decomposition}
Crowdsourcing has explored the decomposition of work for the better part of a decade;
\citeauthor{crowdForgeKittur} specifically
drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

Much of the research in the space of designing crowd work has
sought to illustrate the potential to take highly creative or skilled work
and generate high--quality results.
Perhaps the most notable case study here can be found in
\citeauthor{foundry}'s \textit{Foundry}, which employed
``flash teams'' to accomplish work typically thought of as only within reach of experts
\cite{foundry}.

Research exploring the decomposition of work more generally
--- that is, without the constraint of an employer/requester directing workers ---
has since emerged as well.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
--- of sorts ---
will prove relevant as we trace the literature surrounding piecework.

The work described thus far has explored along myriad paths the ways that
we can manage workers for the purpose of accomplishing complex tasks with
rapidly sourced workers from all over the world.
Critically, the work's defining characteristic involves
the use of the Internet as a medium both 
to coordinate workers, as well as to do the work itself.
But research into the ``decomposition'' of work more generally
illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger
and warned of it in, but they were by no means alone in their warnings
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.

Following this thread of work, it may be said that
much of the work in crowdsourcing has found ways of ``vertically slicing'' work
such that each person is responsible for as small a task as can be made reasonable
--- taking a minute of audio, for instance, and transcribing that.
The findings we take away from the crowdsourcing literature might be summed up as
a number of ways
to break tasks down \cite[see][]{selfsourcingTeevan2014,foundry,crowdForgeKittur} and
measuring the costs as they relate to work completion \&
to a lesser extent to workers
\cite[see][]{measuringCrowdsourcingCheng,cheng2015break,crowdworkFuture,professionalCrowdworkEthics}.

Research into piecework has considered the decomposition of work;
\citeauthor{10.2307/23702539} describes piecework in \citeyear{10.2307/23702539} as
``\dots~based on examination of various shop jobs,
which included calculation of the standard time and compensation for each task.
Most piecework plans required additional clerical and supervisory people
(such as piecework clerks, inspectors, and ``experts'')\dots'',
allowing for what the \textit{American Machinist} would later call ``paper efficiency'',
describing savings on paper that are in fact passed on to workers
\cite{10.2307/23702539}.
In this context,
the introspection of tasks by experts and the careful work assignment \& management of workers
we see in historical piecework seem to parallel crowdsourcing.

% \citeauthor{Brown01041990} draws more decisive boundaries on piece rate approaches to remuneration,
identifying in analysis of data from
the U.S. Bureau of Labor and Statistics that
``larger establishment are less likely to use piece rates and predominantly female establishments more likely to do so; unionized establishments make significantly greater use of standard--rate pay than do nonunion establishments; \textbf{incentive pay is less likely in jobs with a variety of duties than in jobs with a narrow set of routinized duties}; and the ease of monitoring work quality is correlated with the use of incentive pay''
% \cite{Brown01041990}.

What's different today? We can turn to \citeauthor{10.2307/23702539}'s reflection on railroad piecework
for a hint of what might have enabled the future of crowdwork in which we now live:
``\dots~only the largest and most wealthy railroads stood to gain substantially from scientific management,
because only they had the resources to eliminate union resistance and
\textit{pay the overhead involved in installing work reorganization}''
(emphasis added)
\cite{10.2307/23702539}.

We argue that crowdsourcing is more widespread today,
and has the potential to become even larger in scale,
because the underlying architecture of crowdwork is digital;
reformulating workflows to decompose tasks and institute piecework compensation programs
is easier today than it was for railroad companies which had to move physical capital to do so.

\ali{\citeauthor{10.2307/23702539} later argues that a significant obstacle to the introduction of piecework in railroad shops was the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely if ever interact face--to--face and opportunities for coordination and collective action are severely limited,
we should expect to see the challenges stymieing collective action that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.
}

%                     _            _         _                  _   _             
% __      _____  _ __| | __   __ _| |__  ___| |_ _ __ __ _  ___| |_(_) ___  _ __  
% \ \ /\ / / _ \| '__| |/ /  / _` | '_ \/ __| __| '__/ _` |/ __| __| |/ _ \| '_ \ 
%  \ V  V / (_) | |  |   <  | (_| | |_) \__ \ |_| | | (_| | (__| |_| | (_) | | | |
%   \_/\_/ \___/|_|  |_|\_\  \__,_|_.__/|___/\__|_|  \__,_|\___|\__|_|\___/|_| |_|
%

\subsubsection{Work Abstraction}\label{sec:workAbstraction}
Decomposition allows requesters to assign parallelized tasks
without undue concern for the broader context of the work.
The earlier example of transcribed audio is admittedly a carefully curated one
--- used to illustrate the ability
to parallelize work across as many workers as there are tasks ---
but even in this case problems arise;
breaking an hour--long interview into
3,600 1--second--long tasks would seem to make it impossible to do the tasks
for lack of \textit{context},
but the other extreme (one hour--long block)
offers no performance improvement over conventionally sourced work.

The question, then, becomes about how to break tasks down as much as possible
(as discussed in the previous section)
without losing the necessary context to do a task.
Stated another way, how can we design work so that as little context as possible is provided,
without leaving out context or information necessary to complete the task?
As \citeauthor{verroios2014context} frame it,
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.

While some research has attempted to increase workers' awareness of the work they do in
apparent efforts to yield higher quality work,
others have turned this constraint of crowdwork into a feature ---
the abstraction from the work itself
appears to allow requesters to engage workers in work with ---
for instance ---
sensitive, confidential or otherwise personally identifying information.
We will discuss these and other avenues of research here.

\textit{Cascade} demonstrated that it's possible to
break certain classes of tasks apart
in such a way that they yield taxonomies of various subjects,
a task generally thought to be sufficiently complex that only expert workers
with top--down awareness of the task
--- in this case, with awareness of all the constituent colors ---
could complete the task
\cite{chilton2013cascade}.
\citeauthor{verroios2014context} further illustrate this potential by
forming a task one might consider highly contextually dependent
--- summarizing the contents of a movie ---
in such a way that crowd workers could contribute small pieces of work without
needing to know the content of the rest of the project
\cite{verroios2014context}.

%   __ _           _ _     _ _ _ _         
%  / _| | _____  _(_) |__ (_) (_) |_ _   _ 
% | |_| |/ _ \ \/ / | '_ \| | | | __| | | |
% |  _| |  __/>  <| | |_) | | | | |_| |_| |
% |_| |_|\___/_/\_\_|_.__/|_|_|_|\__|\__, |
%                                    |___/

% how much volatility and quality can we deal with?
% how to measure, get rid of people, recover from bad workers
%mason's on getting workers to be better
\subsubsection{Volatile quality and availability? How much can you deal with?}\label{sec:flexibility}
A number of researchers have identified
worker attrition,
variability of worker performance,
and uncertainty about good versus bad--faith actors as open questions of crowdwork
\cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
\ali{We can and should discuss the distinction between presumably ``bad faith'' workers
\& workers who are merely responding in kind to bad requesters
--- and the broader questions surrounding
the roles that requesters as well as workers should play ---
but let it suffice to say that
requesters have been trying to understand and manage what appears to them as inconsistent work.
Their ways of responding to that variance in work quality has largely involved
making the work more flexible and resilient to work
(although some work has gone into investigating the causes, rather than treating the symptoms)}

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance
\cite{cheng2015break}.
This work illustrates a broader sentiment in
both the study and practice
of crowdwork, that microtasks should be designed resiliently against the variability of workers,
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance,
or a good worker's sudden departure,
does not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together
\cite[respectively]{cheng2015break,delayAndOrderLasecki}.

\citeauthor{embracingErrorKrishna} take a different approach;
by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
the authors offer orders--of--magnitude improvements
in various binary classification tasks
% on the principle that diverse workers complete these tasks
% in order to accurately inform the model on the variety of delays in response times.
\cite{embracingErrorKrishna}.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of it instead:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

The work thus far seems to attempt to maximize the quality of work among workers through various means:
\begin{inlinelist}
  \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju},
  \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
  \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
\end{inlinelist}.

% \subsubsection{Piecework's role here}
% We address the question of the limits of crowdsourcing in three parts:
% \begin{inlinelist}
% \item decomposition
% \item work abstraction
% and \item flexibility
% \end{inlinelist}.
% The literature on piecework has offered insights into each of these topics, which we will explore now.

@@

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
  Points to make:
  \begin{itemize}
    \item Blossoming of piecework
    \begin{itemize}
      \item high point: consultants?
      \item most cases: auto workers/etc\dots
      \item worst case: sweatshops (especially in developing nations)
    \end{itemize}
    \item what led to these outcomes?
    \begin{itemize}
      \item ``consultant'' work came out well because the work was complex;
      this made it difficult to turn into a mass market commodity.
      We see consultants ranging skill levels like
      oDesk (implementing modules) to
      Accenture (on--demand teams of consultants).
      \item auto workers,
      working in settings where capital couldn't be moved as easily
      found themselves in the same workspace as a direct
      --- if multi--stepped ---
      result to the benefits of putting people in the same place to consolidate resources.
      Moreover,
      workers had leverage over factory owners as a result of that consolidated capital;
      operating equipment required training.
      \item sweatshop workers fared the worst,
      for reasons that may seem obvious with hindsight.
      Source materials for textiles are easier to ship than mechanical components such as engines,
      making it easier for factories to relocate to developing nations
      (where cost--of--living, and consequently wages, would be lower).
      As wages, CoLAs, and QoL rise, workers begin asking for
      (and later demanding)
      higher wages and better conditions.
      But where the auto workers have leverage,
      textile workers find only a precarious economic balance now tipped by their collective action,
      spurring manufacturers to move to a new locale
    \end{itemize}
  \end{itemize}

@@

    % \section{Case Studies}
    The existing body of research has shed light on on--demand labor from various perspectives,
    and revealed a number of topics that,
    through our framing, are clearly situated together.
    Those topics are, at a high level, as follows:
    \begin{enumerate}
    \item the \textbf{processes} involved in making work into tasks, or discretization;
    \item the outcomes (and indeed the \textbf{fallout}) of that discretization,
    both on the work itself as well as the workers;
    and finally
    \item the \textbf{relationships} between workers and requesters of the work
    --- both \textit{cooperative} and \textit{adversarial} cases.
    \end{enumerate}

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.

  \end{appendices}
  }
